Reproducible Research: A Tutorial on how to do the same thing more than once in R

### 2021-08-04 manuscript.Rmd
cite worcs as a source of PAC
include setup in reproducing a project closes #187

When you or someone else who received your project want to reproduce it, they can ask repro to explain how this should be done:

>>>>

When you or someone else who received your project want to reproduce it, they first have to install the required software, which is Make, and Docker.
Remember, you can use the `check_*`-functions to test if these are installed:

```{r}
check_make()
check_docker()
```

When they are setup, they can ask `repro` to explain how they should use Make and Docker to reproduce the project (or you could explain it to them):
